---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r,error=TRUE}
install.packages("blblm")
library(blblm)
library(furrr)
library(foreach)
library(doParallel)
library(parallel)
library(readr)
library(tidyverse)
```


```{r,error=TRUE,echo=FALSE}
#' @import purrr
#' @import stats
#' @import readr
#' @import furrr
#' @importFrom magrittr %>%
#' @details
#' Linear Regression with Little Bag of Bootstraps
"_PACKAGE"


## quiets concerns of R CMD check re: the .'s that appear in pipelines
# from https://github.com/jennybc/googlesheets/blob/master/R/googlesheets.R
utils::globalVariables(c("."))

#' Parallel bootstrap lm function
#' @description It's a bootstrap lm function that supports parallelization.
#' If you want to use parallel computation, run `plan(multiprocess, workers =cl)` first
#' @param formula Formula for the model
#' @param file_names A list of files(dataframe) you want to work on
#' @param B Number of bootstraps
#' @param cl Number of CPUs you want to use
#' @return A fitted bootstrap model using parallel computation
#' @export
#' @examples
#' par_blblm(mpg ~ wt * hp,file_names=c("mtcars/1.csv","mtcars/2.csv","mtcars/3.csv"),B=1000,cl=3)
par_blblm <- function(formula, file_names, B = 1000) {

  estimates <- future_map(file_names,~{
   df <- read_csv(., col_types = cols())
   lm_each_subsample(formula = formula, data = df, n = nrow(df), B = B)
 })
  res <- list(estimates = estimates, formula = formula)
  class(res) <- "blblm"
  invisible(res)
}



#' bootstrap lm function
#' @description It's a bootstrap glm function
#' @param formula Formula for the model
#' @param file_names A list of files(dataframe) you want to work on
#' @param B Number of bootstraps
#' @return A fitted bootstrap model
#' @export
#' @examples
#' blblm(mpg ~ wt * hp,file_names=c("mtcars/1.csv","mtcars/2.csv","mtcars/3.csv"),B=1000)

blblm <- function(formula, file_names, B = 5000) {
  m <- length(file_names)
  estimates <- map(
     file_names,~{
       df <- read_csv(.,col_types = cols())
    lm_each_subsample(formula = formula, data = df, n = nrow(df), B = B)})
  res <- list(estimates = estimates, formula = formula)
  class(res) <- "blblm"
  invisible(res)
}

#' split data into m parts of approximated equal sizes
split_data <- function(data, m) {
  idx <- sample.int(m, nrow(data), replace = TRUE)
  data %>% split(idx)
}


#' compute the estimates
lm_each_subsample <- function(formula, data, n, B) {
  replicate(B, lm_each_boot(formula, data, n), simplify = FALSE)
}


#' compute the regression estimates for a blb dataset
lm_each_boot <- function(formula, data, n) {
  freqs <- rmultinom(1, n, rep(1, nrow(data)))
  lm1(formula, data, freqs)
}


#' estimate the regression estimates based on given the number of repetitions
lm1 <- function(formula, data, freqs) {
  # drop the original closure of formula,
  # otherwise the formula will pick a wront variable from the global scope.
  environment(formula) <- environment()
  fit <- lm(formula, data, weights = freqs)
  list(coef = blbcoef(fit), sigma = blbsigma(fit))
}


#' compute the coefficients from fit
blbcoef <- function(fit) {
  coef(fit)
}


#' compute sigma from fit
blbsigma <- function(fit) {
  p <- fit$rank
  y <- model.extract(fit$model, "response")
  e <- fitted(fit) - y
  w <- fit$weights
  sqrt(sum(w * (e^2)) / (sum(w) - p))
}

#' Print fit formula
#' @description Print the fit formula
#' @param x fit
#' @return Fit formula
#' @export
#' @method print blblm
#' @examples
#' print(fit)
print.blblm <- function(x, ...) {
  cat("blblm model:", capture.output(x$formula))
  cat("\n")
}

#' Print sigma
#' @description Print the sigma of fit
#' @param object fit
#' @param confidence Whether to calculate confidence interval
#' @param level confidence level
#' @return Sigma of the fit
#' @export
#' @method sigma blblm
#' @examples
#' sigma(fit,confidence=TRUE,level=0.95)
sigma.blblm <- function(object, confidence = FALSE, level = 0.95, ...) {
  est <- object$estimates
  sigma <- mean(map_dbl(est, ~ mean(map_dbl(., "sigma"))))
  if (confidence) {
    alpha <- 1 - 0.95
    limits <- est %>%
      map_mean(~ quantile(map_dbl(., "sigma"), c(alpha / 2, 1 - alpha / 2))) %>%
      set_names(NULL)
    return(c(sigma = sigma, lwr = limits[1], upr = limits[2]))
  } else {
    return(sigma)
  }
}


#' coefficients of fit
#' @description Print the coefficients of fit
#' @param object fit
#' @return coefficients
#' @export
#' @method coef blblm
#' @examples
#' coef(fit)
coef.blblm <- function(object, ...) {
  est <- object$estimates
  map_mean(est, ~ map_cbind(., "coef") %>% rowMeans())
}



#' Confidence interval of fit
#' @description Print the confidence interval of fit
#' @param object fit
#' @param level confidence level
#' @return coefficients
#' @export
#' @method confint blblm
#' @examples
#' confint(fit,parm=NULL,level=0.95)
confint.blblm <- function(object, parm = NULL, level = 0.95, ...) {
  if (is.null(parm)) {
    parm <- attr(terms(fit$formula), "term.labels")
  }
  alpha <- 1 - level
  est <- object$estimates
  out <- map_rbind(parm, function(p) {
    map_mean(est, ~ map_dbl(., list("coef", p)) %>% quantile(c(alpha / 2, 1 - alpha / 2)))
  })
  if (is.vector(out)) {
    out <- as.matrix(t(out))
  }
  dimnames(out)[[1]] <- parm
  out
}

#' Predict the model
#' @description Predict the fitted model
#' @param object fit
#' @param new_data The data you want to predict
#' @param level confidence level
#' @return coefficients
#' @export
#' @method predict blblm
#' @examples
#' predict(object, new_data, confidence = TRUE, level = 0.95)
predict.blblm <- function(object, new_data, confidence = FALSE, level = 0.95, ...) {
  est <- object$estimates
  X <- model.matrix(reformulate(attr(terms(object$formula), "term.labels")), new_data)
  if (confidence) {
    map_mean(est, ~ map_cbind(., ~ X %*% .$coef) %>%
      apply(1, mean_lwr_upr, level = level) %>%
      t())
  } else {
    map_mean(est, ~ map_cbind(., ~ X %*% .$coef) %>% rowMeans())
  }
}


mean_lwr_upr <- function(x, level = 0.95) {
  alpha <- 1 - level
  c(fit = mean(x), quantile(x, c(alpha / 2, 1 - alpha / 2)) %>% set_names(c("lwr", "upr")))
}

map_mean <- function(.x, .f, ...) {
  (map(.x, .f, ...) %>% reduce(`+`)) / length(.x)
}

map_cbind <- function(.x, .f, ...) {
  map(.x, .f, ...) %>% reduce(cbind)
}

map_rbind <- function(.x, .f, ...) {
  map(.x, .f, ...) %>% reduce(rbind)
}
#######################################
glm1 <- function(formula, data, freqs) {
  # drop the original closure of formula,
  # otherwise the formula will pick a wront variable from the global scope.
  environment(formula) <- environment()
  fit <- glm(formula, family = binomial(link = "logit"), data, weights = freqs)
  list(coef = blbcoef(fit))
}

glm_each_boot <- function(formula, data, n) {
  freqs <- rmultinom(1, n, rep(1, nrow(data)))
  glm1(formula, data, freqs)
}

glm_each_subsample <- function(formula, data, n, B) {
  replicate(B, glm_each_boot(formula, data, n), simplify = FALSE)
}




#' Parallel bootstrap glm function
#' @description It's a bootstrap glm function that supports parallelization.
#' If you want to use parallel computation, run `plan(multiprocess, workers =cl)` first
#' @param formula Formula for the model
#' @param file_names A list of files(dataframe) you want to work on
#' @param B Number of bootstraps
#' @param cl Number of CPUs you want to use
#' @return A fitted bootstrap model using parallel computation
#' @export
#' @examples
#' par_blbglm(mpg ~ wt * hp,file_names=c("mtcars/1.csv","mtcars/2.csv","mtcars/3.csv"),B=1000,cl=3)
par_blbglm <- function(formula, file_names, B = 1000,cl=1) {
  estimates <- future_map(file_names,~{
    df <- read_csv(., col_types = cols())
    glm_each_subsample(formula = formula, data = df, n = nrow(df), B = B)
  })
  res <- list(estimates = estimates, formula = formula)
  class(res) <- "blblm"
  invisible(res)
}


#' bootstrap glm function
#' @description It's a bootstrap glm function
#' @param formula Formula for the model
#' @param file_names A list of files(dataframe) you want to work on
#' @param B Number of bootstraps
#' @return A fitted bootstrap model
#' @export
#' @examples
#' blbglm(mpg ~ wt * hp,file_names=c("mtcars/1.csv","mtcars/2.csv","mtcars/3.csv"),B=1000)
blbglm <- function(formula, file_names, B = 5000) {
  m <- length(file_names)
  estimates <- map(
    file_names,~{
      df <- read_csv(.,col_types = cols())
      glm_each_subsample(formula = formula, data = df, n = nrow(df), B = B)})
  res <- list(estimates = estimates, formula = formula)
  class(res) <- "blblm"
  invisible(res)
}

#' Predict categorical variables
#' @description
#' @param fit A fit generated by blblm
#' @param testdatas A dataframe contain the variables you want to use to predict
#' @param confidence Whether you want to use confidence interval
#' @return The probabilities of predicting categorical variables
#' @method confident blbglm
#' @export
predict.blbglm <- function(fit, testdata, confidence = FALSE){
  coef <- map(fit$estimates, ~map(., "coef") %>% reduce(., rbind))
  X<-model.matrix(reformulate(attr(terms(fit$formula), "term.labels")), testdata)
  t<-map(coef,~apply(.,1,function(y)X%*%y))%>%
    map(.,rowMeans)
    t <- reduce(t,`+`)/length(t)
  if(confidence){
    map(coef,~apply(.,1,function(y)X%*%y))%>%
      map(.,data.frame)%>%
      map(.,~apply(.,1,function(x)exp(x)/(1+exp(x))))%>%
      map(.,~apply(.,2,function(x)quantile(x,c(0.025,0.975))))%>%
      reduce(`+`)/length(coef)
  }
  else{
    print(exp(t)/(1+exp(t)))}
}

```

```{r}
m <- 3
groups <- sample(seq_len(m), nrow(mtcars), replace = TRUE)
mtcars$group <- groups
dir.create("mtcars/", showWarnings = FALSE)
# for (i in seq_len(m)) {
#   write_csv(mtcars[which(mtcars$group==i),], str_c("mtcars/", i, ".csv"))
# }
file_names <- file.path("mtcars", list.files("mtcars"))
```


I did some improvements to the function `blblm`. I allow users to specify a list of file names to run the model.
```{r}
fit1 <- blblm(mpg ~ wt,file_names,B=2000)
coef(fit1)
sigma(fit1)
confint(fit1, "wt")
predict(fit1, data.frame(wt = c(2.5, 3,3.5)),confidence=TRUE)
```
I created a `par_blblm` funtion, which allow users to do the parallel computation. Users can decide how many CPUs they want to use in the computation.

`par_blblm` require users to make clusters so that they can use more CPUs.
Make clusters
```{r,error=TRUE}
suppressWarnings(plan(multiprocess, workers =4))
```
```{r}
fit2 <- par_blblm(mpg ~ wt,file_names,B=2000)
coef(fit2)
sigma(fit2)
confint(fit2, "wt")
predict(fit2, data.frame(wt = c(2.5, 3,3.5)),confidence=TRUE)
```
I use `bench::mark to compare` their efficiency. `par_blblm` is much faster, and using less memory:
```{r}
bench::mark(blblm(mpg ~ wt,file_names,B=2000),
            par_blblm(mpg ~ wt,file_names,B=2000),
            check=FALSE)
```

I also introduced `blbglm` function, which is more powerful than `blblm`
```{r,error=TRUE}
suppressWarnings(fit3 <- blbglm(vs ~ wt,file_names,B=1000))
coef(fit3)
confint(fit3, "wt")
predict(fit3, data.frame(wt = c(2.5, 3,3.5)),confidence=TRUE)
```
Also `par_blbglm` function
```{r,error=TRUE}
suppressWarnings(fit4 <- par_blbglm(am ~ hp,file_names,B=1000))
coef(fit4)
confint(fit4, "hp")
predict(fit4, data.frame(hp = c(150,200)),confidence=TRUE)
```

Function `predict.blbglm` can predict categorical variables and return their probabilities
```{r}
fit5 <- blblm(am ~ wt*disp,file_names,B=50)
predict.blbglm(fit5, data.frame(wt = c(2.5, 3,3.5,4,4.5,5),disp=c(150,160,220,140,170,180)),confidence=FALSE)
```

